Meta-analysis

### 2020-06-22 04_MetaAnalysis.Rmd
Markdown syntax, USQ colours and histograms, suppress long outputs

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer,metafor, netmeta)

@@

# Data
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
```

@@

   - Grain yield is our response variable and will be converted to Kg / Ha.  
   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept.  
   - We will test spray management (our treatment) as a fixed effect and random slope to trial.

@@

m11 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)

```

@@

```{r m9_vs_m10}
anova(m9, m10) # m9 is significantly better model
```
There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.

@@

There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`

@@

#### Imputing sample variances from Mean squares
```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
hist_usq(unique(slimmer_PM_dat$Y_Msquare))
hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution

```

@@

```{r imputing_MSE, eval=FALSE, include=FALSE}
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref,location,year)%>%
   summarise(unique(Y_Msquare))

@@

```{r imputation_MSE, eval=FALSE, include=FALSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

@@

```{r remove_yieldErrorNAs}
slimmer_PM_dat <- 
   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]

```

@@

```{r table_of_nTreatments}
kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
                  align = rep('c', 8),
      caption = "Which treatments and how many treatments are represented in each year") %>%  
   kable_styling(
      "striped",
      fixed_thead = TRUE,
      full_width = FALSE,
      position = "center"
   )
```
Treatments Late_plus and early don't have very good comparison to other treatments.

@@

```{r treatment_means_plot}
# class spray_management as a factor and reorder them for the plot
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3,4))])

@@

There seems like little difference between the treatments, with exception to Late_plus. 
Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study.  
This should reduce variation in yield due between trials.

@@

Using the mean difference in the treatment effect seems to show the impact of each treatment better than just raw yield and reduces the variability in the treatments.
We know there is a good deal of variability in our studies and between them. 
Mungbean produces variable yields between seasons so we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
Let's calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.

@@

Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
Let's show the rational for our calculation and then add a secondary variance column (`vi2`)

$MSE = Var + bias$  
However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:  
$MSE = Var$

To calculate the sample variance (for each treatment in the tria) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
We can show this because:  
$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$  
Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).

@@

```{r MSE_2_SVar}
#calculation when using log of response
# slimmer_PM_dat$vi <-
#    slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
#                                   2)
#
slimmer_PM_dat$vi2 <- 
   slimmer_PM_dat$Y_Msquare / 
   slimmer_PM_dat$n

```

@@

Let's calculate standardised mean differences and add them to the data frame.
```{r StandardisedMeanDifference}
slimmer_PM_dat$pooledSD <- NA
slimmer_PM_dat$vi_C <- NA
for(T_ref in slimmer_PM_dat$trial_ref){

   # First we need to Calculate the pooled standard deviation
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <- 
   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yield_error"])/
           (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))

   # Then Create a column with the value of the mean grain yield of the no spray control for comparisons to the treatments means
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yi_C"] <-  
      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref &
                        slimmer_PM_dat$fungicide_ai == "control",
                        "grain_yield.t.ha"], na.rm = TRUE)

}
# Calculate standardised mean difference
slimmer_PM_dat$grain_SMD <- (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C)/ slimmer_PM_dat$pooledSD

```

@@

Let's simplify our data
```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
      spray_management,
      c( "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )))%>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
   )
```

## Meta-analysis  
### metafor package  
Let's inspect the data to determine if we need to transform the response variable

```{r}
hist(dat1$grain_yield.t.ha)
hist(log(dat1$grain_yield.t.ha))
hist(sqrt(dat1$grain_yield.t.ha))
hist(dat1$grain_SMD)
```
Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or sqrt will not work on negative values.

Let's undertake the meta-analysis using the package `metafor`.
Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management -1,
   method = "ML",
   random = ~ spray_management|trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010]. 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

```{r rma_noRandomInteractiveTerm}

PM_mv_St <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1|trial),
   data = dat1
)

AIC(PM_mv_St)
anova(PM_mv, PM_mv_St)
```
The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model `PM_mv`.

@@

The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different to zero, or the no spray control.

### Profile plots  
Let's inspect the profile plots to ensure the model is not over-fitted. 
We expect to see the estimate align with the peak of the curve. 
Also that the shape of the line is a curve.  
Caution! this will take some time to run.

```{r}
profile(PM_mv , tau2 = 1)
profile(PM_mv , tau2 = 2)
profile(PM_mv , tau2 = 3)
profile(PM_mv , tau2 = 4)
profile(PM_mv , tau2 = 5)
```

*****
### Metafor comparisons

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
meta_cont <- anova(PM_mv, L = rbind(
   c(-1, 1, 0, 0,0),
   c(-1, 0, 1, 0,0),
   c(-1, 0, 0, 1,0),
   c(-1, 0, 0, 0,1),
   c(0, -1, 1, 0,0),
   c(0, -1, 0, 1,0),
   c(0, -1, 0, 0,1),
   c(0, 0, -1, 1,0),
   c(0, 0, -1, 0,1),
   c(0, 0, 0, -1,1)
   ))

change_labels <- function(x1){
   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
   x1
}

@@

data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
      estimates = meta_cont$Lb,
      se = meta_cont$se,
      z_val = meta_cont$zval,
      pval = meta_cont$pval,
      VisP = p_star(meta_cont$pval))
```
Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
`Late_plus` is estimated as saving the most yield compared and is significantly higher than all other treatments except `recommended_plus`.  
Let's view these comparisons in a plot.

First we will format the results into a data frame.
```{r metafor_results}
results_AI <- data.frame(cbind(PM_mv$b,
                               PM_mv$ci.lb,
                               PM_mv$ci.ub))

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(
      c( "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   )

@@

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5,1.5, by = 0.2),
      color = "grey80",
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

@@

### netmeta package  
Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust. The `netmeta` package uses a frequentist approach to the analysis and focuses on the pairwise comparisons between treatments.

@@

summary(net_con)
```
Now let's visualise this as a forest plot

```{r netmeta-forest}
# I don't know why this is not working I will need to follow up on this
forest(
   net_con,
   reference.group = 5,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)

```

The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray control. It estimates the mean is very similar to the recommended treatments. The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.

```{r netgraphGW}
netgraph(
   net_con,
   plastic = FALSE,
   col = "orange",
   thickness =  "number.of.studies",
   points = FALSE,
   col.points = "black",
   cex.points = 1,
   number.of.studies = TRUE,
   cex.number.of.studies = 1,
   col.number.of.studies = "black",
   bg.number.of.studies = "orange",
   multiarm = FALSE,
   col.multiarm = "lightblue",
   pos.number.of.studies = 0.5
)
```

>>>>

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               lme4,
               RColorBrewer,
               metafor,
               netmeta)

@@

# Data
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
)
```

@@

To do this, in our model:

   - Grain yield is our response variable and will be converted to kg / ha

   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept

   - We will test spray management (our treatment) as a fixed effect and random slope to trial

@@

m11 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)
```

@@

```{r m9_vs_m10}
anova(m9, m10) # m9 is significantly better model
```

There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.

@@

There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`).

@@

#### Imputing sample variances from Mean squares

```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
hist_usq(unique(slimmer_PM_dat$Y_Msquare))
hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
```

@@

```{r imputing_MSE, eval=FALSE, include=FALSE}
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref, location, year) %>%
   summarise(unique(Y_Msquare))

@@

```{r imputation_MSE, eval=FALSE, include=FALSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

@@

```{r remove_yieldErrorNAs}
slimmer_PM_dat <- 
   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
```

@@

```{r table_of_nTreatments}
kable(
   table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
   align = rep('c', 8),
   caption = "Which treatments and how many treatments are represented in each year"
) %>%
   kable_styling(
      "striped",
      fixed_thead = TRUE,
      full_width = FALSE,
      position = "center"
   )
```

Treatments Late_plus and early don't have very good comparison to other treatments.

@@

```{r treatment_means_plot}
# class spray_management as a factor and reorder them for the plot
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3, 4))])

@@

There seems like little difference between the treatments, with exception to `Late_plus`.
Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study, this should reduce variation in yield due between trials.

@@

Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
We know there is a good deal of variability in our studies and between them.
Mungbean produces variable yields between seasons so we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
Let's calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.

@@

Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
Let's show the rational for our calculation and then add a secondary variance column (`vi2`).

$MSE = Var + bias$

However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:

$MSE = Var$

To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
We can show this because:
$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$
Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).

@@

```{r MSE_2_SVar}
#calculation when using log of response
# slimmer_PM_dat$vi <-
#    slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
#                                   2)
#
slimmer_PM_dat$vi2 <- 
   slimmer_PM_dat$Y_Msquare / 
   slimmer_PM_dat$n
```

@@

Let's calculate standardised mean differences and add them to the data frame.

```{r StandardisedMeanDifference}
slimmer_PM_dat$pooledSD <- NA
slimmer_PM_dat$vi_C <- NA
for (T_ref in slimmer_PM_dat$trial_ref) {
   # First we need to Calculate the pooled standard deviation
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <-
      sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"] - 1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yield_error"]) /
              (sum(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"]) - nrow(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,])))

   # Then Create a column with the value of the mean grain yield of the no spray control for comparisons to the treatments means
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yi_C"] <-
      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref &
                             slimmer_PM_dat$fungicide_ai == "control",
                          "grain_yield.t.ha"], na.rm = TRUE)

}
# Calculate standardised mean difference
slimmer_PM_dat$grain_SMD <-
   (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C) / slimmer_PM_dat$pooledSD 
```

@@

Let's simplify our data.

```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             )) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
   )
```

## Meta-analysis

### metafor package

Let's inspect the data to determine if we need to transform the response variable.

```{r}
hist_usq(dat1$grain_yield.t.ha)
hist_usq(log(dat1$grain_yield.t.ha))
hist_usq(sqrt(dat1$grain_yield.t.ha))
hist_usq(dat1$grain_SMD)
```

Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or square root will not work on negative values.

Let's undertake the meta-analysis using the package `metafor`.
Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

```{r rma_noRandomInteractiveTerm}
PM_mv_St <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1|trial),
   data = dat1
)

AIC(PM_mv_St)
anova(PM_mv, PM_mv_St)
```

The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`.
So we will keep the original model `PM_mv`.

@@

The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different from zero, or the no spray control.

### Profile plots

Let's inspect the profile plots to ensure the model is not over-fitted. 
We expect to see the estimate align with the peak of the curve. 
Also that the shape of the line is a curve.
Caution! this will take some time to run.

```{r profile_plots, message=FALSE, results="hide"}
profile(PM_mv, tau2 = 1)
profile(PM_mv, tau2 = 2)
profile(PM_mv, tau2 = 3)
profile(PM_mv, tau2 = 4)
profile(PM_mv, tau2 = 5)
```

*****

### Metafor comparisons

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.

```{r metafor_contrasts}
meta_cont <- anova(PM_mv, L = rbind(
   c(-1, 1, 0, 0, 0),
   c(-1, 0, 1, 0, 0),
   c(-1, 0, 0, 1, 0),
   c(-1, 0, 0, 0, 1),
   c(0, -1, 1, 0, 0),
   c(0, -1, 0, 1, 0),
   c(0, -1, 0, 0, 1),
   c(0, 0, -1, 1, 0),
   c(0, 0, -1, 0, 1),
   c(0, 0, 0, -1, 1)
))

change_labels <- function(x1) {
   x1 <- gsub(pattern = "spray_management",
              replacement = "",
              x = x1)
   x1
}

@@

data.frame(
   contrasts = change_labels(meta_cont$hyp[, 1]),
   estimates = meta_cont$Lb,
   se = meta_cont$se,
   z_val = meta_cont$zval,
   pval = meta_cont$pval,
   VisP = p_star(meta_cont$pval)
)
```

Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
`Late_plus` is estimated as saving the most yield compared and is significantly higher than all other treatments except `recommended_plus`.
Let's view these comparisons in a plot.

First we will format the results into a data frame.

```{r metafor_results}
results_AI <- data.frame(cbind(PM_mv$b,
                               PM_mv$ci.lb,
                               PM_mv$ci.ub))

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(c(
      "Early",
      "Recommended",
      "Recommended_plus",
      "Late",
      "Late_plus"
   ))

@@

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5, 1.5, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

@@

### netmeta package

Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
The `netmeta` package uses a frequentist approach to the analysis and focuses on the pairwise comparisons between treatments.

@@

summary(net_con)
```

Now let's visualise this as a forest plot.

```{r netmeta-forest}
forest(
   net_con,
   reference.group = 5,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)
```

The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray control.
It estimates the mean is very similar to the recommended treatments.
The recommended plus and late_plus treatments show higher mean estimates, however are not significantly different from the early estimate.

```{r netgraphGW}
netgraph(
   net_con,
   plastic = FALSE,
   col = usq_cols("support orange"),
   thickness =  "number.of.studies",
   points = FALSE,
   col.points = usq_cols("usq charcoal"),
   cex.points = 1,
   number.of.studies = TRUE,
   cex.number.of.studies = 1,
   col.number.of.studies = "black",
   bg.number.of.studies = usq_cols("support orange"),
   multiarm = FALSE,
   col.multiarm = usq_cols("support turquiose"),
   pos.number.of.studies = 0.5
)
```
